### 2025-03-14 paper/quarto_ecml/paper.tex
Add description of datasets
TODO Patrick: (1) put images of synthetic datasets in the appendix, (2) is "Cred" the Default of Credit Card Clients?

We run the experiments with three gradient-based generators:
\emph{Generic} of \cite{wachter2017counterfactual} as a simple baseline
approach, \emph{REVISE} \cite{joshi2019realistic} that aims to generate
plausible counterfactuals using a surrogate Variational Autoencoder
(VAE), and \emph{ECCo}---the generator of \cite{altmeyer2024faithful}
but without the conformal prediction component---as a method that
directly targets both faithfulness and plausibility of the CEs.

>>>>

We run the experiments with three gradient-based generators:
\emph{Generic} of \cite{wachter2017counterfactual} as a simple baseline
approach, \emph{REVISE} \cite{joshi2019realistic} that aims to generate
plausible counterfactuals using a surrogate Variational Autoencoder
(VAE), and \emph{ECCo}---the generator of \cite{altmeyer2024faithful}
but without the conformal prediction component---as a method that
directly targets both faithfulness and plausibility of the
counterfactuals.

We make use of nine classification datasets common in the CE/AR
literature. Four of them are synthetic with two classes and different
characteristics: linearly separable clusters (\emph{LS}), overlapping
clusters (\emph{OL}), concentric circles (\emph{Circ}), and interlocking
moons (\emph{Moon}). These datasets are generated using the library of
\cite{altmeyer2023explaining} and we present them in the supplementary
appendix. Next, we have four real-world binary tabular datasets from the
domain of economics: \emph{Adult} (a.k.a. Census data) of
\cite{becker1996adult2}, California housing (\emph{CH}) of
\cite{pace1997sparse}, Default of Credit Card Clients (\emph{Cred}) of
\cite{yeh2016default}, and Give Me Some Credit (\emph{GMSC}) of
\cite{kaggle2011give2}. Finally, for the convenience of illustration, we
use of the 10-class \emph{MNIST} vision dataset \cite{lecun1998mnist}.

### 2025-03-14 paper/sections/experiments.qmd
Add description of datasets
TODO Patrick: (1) put images of synthetic datasets in the appendix, (2) is "Cred" the Default of Credit Card Clients?

We run the experiments with three gradient-based generators: *Generic* of @wachter2017counterfactual as a simple baseline approach, *REVISE* [@joshi2019realistic] that aims to generate plausible counterfactuals using a surrogate Variational Autoencoder (VAE), and *ECCo*---the generator of @altmeyer2024faithful but without the conformal prediction component---as a method that directly targets both faithfulness and plausibility of the CEs.

>>>>

We run the experiments with three gradient-based generators: *Generic* of @wachter2017counterfactual as a simple baseline approach, *REVISE* [@joshi2019realistic] that aims to generate plausible counterfactuals using a surrogate Variational Autoencoder (VAE), and *ECCo*---the generator of @altmeyer2024faithful but without the conformal prediction component---as a method that directly targets both faithfulness and plausibility of the counterfactuals.

We make use of nine classification datasets common in the CE/AR literature. Four of them are synthetic with two classes and different characteristics: linearly separable clusters (*LS*), overlapping clusters (*OL*), concentric circles (*Circ*), and interlocking moons (*Moon*). These datasets are generated using the library of [@altmeyer2023explaining] and we present them in the supplementary appendix. Next, we have four real-world binary tabular datasets from the domain of economics: *Adult* (a.k.a. Census data) of [@becker1996adult2], California housing (*CH*) of [@pace1997sparse], Default of Credit Card Clients (*Cred*) of [@yeh2016default], and Give Me Some Credit (*GMSC*) of [@kaggle2011give2]. Finally, for the convenience of illustration, we use of the 10-class *MNIST* vision dataset [@lecun1998mnist].
